Fourmile Calibrations and Output

### 2025-02-27 params.Rmd
minor

ggplot(combo, aes(x = burn, y = value, fill = input_data)) +
  geom_boxplot(alpha = 0.8, outlier.colour = "black") +
  geom_text(aes(label = letter, y = y_text), 
            position = position_dodge(width = 0.75),  # Align with boxplots
            size = 6, 
            vjust = 0) +  # Prevent overlap with whiskers
  facet_wrap(~param, scales = 'free_y') +
  labs(y = element_blank(), x = element_blank()) +
  theme_bw(base_size = 20) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
  theme(
    legend.position = 'bottom',
    legend.text = element_text(size = 16),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black")
  ) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))

>>>>

ggplot(combo, aes(x = burn, y = value, fill = input_data)) +
  geom_boxplot(alpha = 0.8, outlier.colour = "black") +
  geom_text(aes(label = letter, y = y_text), 
            position = position_dodge(width = 0.75),  # Align with boxplots
            size = 6, 
            vjust = 0) +  
  facet_wrap(~param, scales = 'free_y') +
  labs(y = element_blank(), x = element_blank()) +
  theme_bw(base_size = 20) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
  theme(
    legend.position = 'bottom',
    legend.text = element_text(size = 16),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black")
  ) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))
